\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-05-23 chapters/1_intro.tex
Update tables

With our comparison experiments, performed both on 2D urban scenes from the CityScapes dataset and 3D electron microscopy image volumes of neurons, we evaluate the properties of the algorithms in our framework, focusing on their efficiency, robustness and tendency to over- or under-cluster.
Our findings show that one of the new agglomerative algorithms introduced by our generalized framework, based on an average linkage criterion, consistently outperforms all other previously known agglomerative algorithms for signed graphs and achieves competitive scores on the challenging CREMI 2016 segmentation benchmark.
% This simple agglomerative algorithm also achieves competitive scores on the challenging CREMI 2016 segmentation benchmark, similarly to other approaches that rely on complex multi-step pipelines.

\begin{figure}[t]
\centering
% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
\includegraphics[width=0.95\textwidth]{./figs/intro_image_v3.pdf} % left bottom right top
\caption{ Pipeline description: \textbf{(1)} Raw data from the CREMI 2016 neuron-segmentation challenge. \textbf{(2)} Some short- and long-range predictions of our UNet model, where white pixels represent boundary evidence. \textbf{(3)} Outputs of three different agglomerative algorithms included in our proposed generalized clustering framework. The final clustering / instance segmentation is shown in 3a, overlaid with the raw image.  The  agglomeration order in 3b shows which pairs of neighboring pixels were merged first (white), later on (brown), or never (black). In 3c, we also illustrate some iterations of the algorithms on toy graph examples with attractive/positive (green) and repulsive/negative (red) interactions. At each iteration, the yellow edge with highest interaction is contracted (orange arrows), until only negative edges are left.
%We note how similar linkage criteria, like \emph{Sum} (in the middle) and \emph{Average} (on the right), lead to strongly different merging orders. 
% On the left: a single cluster is returned with only attractive interactions.
 % main ideas and contributions
\label{fig:intro_figure}}
\end{figure}

>>>>

With our comparison experiments, performed both on 2D urban scenes from the CityScapes dataset and 3D electron microscopy image volumes of neurons, we evaluate the properties of the algorithms in our framework, focusing on their efficiency, robustness and tendency to over- or under-cluster.
We show that one of the new algorithms derived from our framework, based on an average linkage criterion, outperforms the previously known agglomeration methods expressed in the framework. It also achieves competitive performance on the challenging CREMI 2016 segmentation benchmark.
% This simple agglomerative algorithm also achieves competitive scores on the challenging CREMI 2016 segmentation benchmark, similarly to other approaches that rely on complex multi-step pipelines.

\begin{figure}[t]
\centering
% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
\includegraphics[width=0.95\textwidth]{./figs/intro_image_v3.pdf} % left bottom right top
\caption{ Pipeline description: \textbf{(1)} Raw data from the CREMI 2016 neuron-segmentation challenge. \textbf{(2)} Some short- and long-range predictions of our UNet model, where white pixels represent boundary evidence. \textbf{(3)} Outputs of two agglomerative algorithms included in our proposed generalized clustering framework, with \emph{Sum} and \emph{Average} linkage criteria. The final clustering / instance segmentation is shown in 3a, overlaid with the raw image.  The  agglomeration order in 3b shows which pairs of neighboring pixels were merged first (white), later on (brown), or never (black). In 3c, we also illustrate some iterations of the algorithms on toy graph examples with attractive/positive (green) and repulsive/negative (red) interactions. At each iteration, the yellow edge with highest interaction is contracted (orange arrows), until only negative edges are left in the graph.
%We note how similar linkage criteria, like \emph{Sum} (in the middle) and \emph{Average} (on the right), lead to strongly different merging orders. 
% On the left: a single cluster is returned with only attractive interactions.
 % main ideas and contributions
\label{fig:intro_figure}}
\end{figure}

### 2019-05-23 chapters/5_experiments_cityscapes.tex
Update tables

% !TEX root = ../agglo_clust_review.tex
\section{Experiments on CityScapes}\label{sec:cityscapes_exp}
We also evaluate the performances of \algname{} on the CityScapes dataset \cite{cordts2016cityscapes}, which consists of 5000 street-scene images: 2975 for training, 500 for validation and 1525 for testing.
% recorded by car-mounted cameras with resolution 1024$\times$2048: 2975 images for training, 500 for validation and 1525 for testing. Objects with instance-level annotations belong to the following classes: person, rider, car, truck, bus, train, motorcycle, bicycle. 
See Appendix \ref{sec:appendix_cityscapes} for more details on how we fine-tuned the state-of-the-art proposal-free pipeline proposed in GMIS \cite{liu2018affinity} by using a \emph{S\o resen-Dice} loss, similarly to \cite{wolf2018mutex}.
%that achieved superior performances compared to other proposal-based methods like Mark R-CNN and employs a similar model to the one applied by us on neuron-segmentation.
% Their trained model was made publicly available, so we simply replaced their final graph-merging algorithm (MultiStepHAC) with \algname{}.  their instance branch model by using a \emph{S\o resen-Dice} loss similarly to \cite{wolf2018mutex} and obtained in this way sharper affinity-predictions.
Results are summarized in Table \ref{tab:results_cityscapes_val} and Fig. \ref{fig:cityscapes}: similarly to the previous experiments, \algname{} with \emph{Average} linkage achieves the best scores, whereas other linkage tend to over-cluster, like \emph{Abs. Max.}, or under-cluster and merge instances, like \emph{Sum}. The graph-merging algorithm proposed by \cite{liu2018affinity} (MultiStepHAC) requires the user to tune several threshold parameters and it was probably tailored to the original affinities predicted by them, so it did not generalize well to our fine-tuned model and it achieved lower scores compared to the original AP value of 34.1 reported in \cite{liu2018affinity}.  
Appendix - Table \ref{tab:extended_results_cityscapes_val} includes the scores of all other tested \algname{} algorithms.
\begin{figure}[t]
\centering
\begin{minipage}[b]{0.5\textwidth}
    \centering
    \scriptsize
        \begin{tabular}{l|l|cc}
           & Agglomeration  &  \multicolumn{2}{c}{Use constraints:} \\
          Pipeline & method & \textsc{No} & \textsc{Yes} \\ \midrule
DWT \cite{bai2017deep} & - & 21.2 & - \\
SGN \cite{liu2017sgn} & - & 29.2 & - \\
Mask RCNN \cite{he2017mask} & - & 31.5 & - \\ \hline
 & \textbf{\algname{} Avg-Link}& \textbf{34.3}  & 33.9  \\
\multirow{2}{*}{GMIS \cite{liu2018affinity}} & MultiStepHAC \cite{liu2018affinity} & 33.0 & -  \\
 % & \algname{} Max &   24.3  &   32.5  \\
 & \algname{} Abs. Max. \cite{wolf2018mutex}  & 32.1 & 32.1 \\
 & \algname{} Sum \cite{keuper2015efficient,levinkov2017comparative} & 31.3  & 31.9  \\
 % & \algname{} Min &  0    & 0  \\
        \end{tabular}
    \captionof{table}{Average Precision (AP) scores (higher is better) on the CityScapes validation set.}
    \label{tab:results_cityscapes_val}
\end{minipage}\hfill
\begin{minipage}[b]{0.46\textwidth}
    \centering
\includegraphics[width=\textwidth]{./figs/cityscapes_compare_3.pdf} % left bottom right top
\caption{Instance segmentations given by different \algname{} linkage criteria on CityScapes}\label{fig:cityscapes}
\end{minipage}
\end{figure}

>>>>

% !TEX root = ../agglo_clust_review.tex
\section{Experiments on CityScapes}\label{sec:cityscapes_exp}
We also evaluate the performances of \algname{} on the CityScapes dataset \cite{cordts2016cityscapes}, which consists of 5000 street-scene images: 2975 for training, 500 for validation and 1525 for testing.
% recorded by car-mounted cameras with resolution 1024$\times$2048: 2975 images for training, 500 for validation and 1525 for testing. Objects with instance-level annotations belong to the following classes: person, rider, car, truck, bus, train, motorcycle, bicycle. 
See Appendix \ref{sec:appendix_cityscapes} for more details on how we fine-tuned the state-of-the-art proposal-free pipeline proposed in GMIS \cite{liu2018affinity} by using a \emph{S\o resen-Dice} loss, similarly to \cite{wolf2018mutex}.
%that achieved superior performances compared to other proposal-based methods like Mark R-CNN and employs a similar model to the one applied by us on neuron-segmentation.
% Their trained model was made publicly available, so we simply replaced their final graph-merging algorithm (MultiStepHAC) with \algname{}.  their instance branch model by using a \emph{S\o resen-Dice} loss similarly to \cite{wolf2018mutex} and obtained in this way sharper affinity-predictions.
Results are summarized in Table \ref{tab:results_cityscapes_val} and Fig. \ref{fig:cityscapes}: similarly to the previous experiments, \algname{} with \emph{Average} linkage achieves the best scores, whereas other linkage tend to over-cluster, like \emph{Abs. Max.}, or under-cluster and merge instances, like \emph{Sum}. The graph-merging algorithm proposed by \cite{liu2018affinity} (MultiStepHAC) requires the user to tune several threshold parameters and it was probably tailored to the original affinities predicted by them, so it did not generalize well to our fine-tuned model and it achieved lower scores compared to the original AP value of 34.1 reported in \cite{liu2018affinity}.  
Appendix - Table \ref{tab:extended_results_cityscapes_val} includes the scores of all other tested \algname{} algorithms.
\begin{figure}[t]
\centering
\begin{minipage}[b]{0.5\textwidth}
    \centering
    \scriptsize
        \begin{tabular}{l|l|cc}
           & Agglomeration  &  \multicolumn{2}{c}{Use constraints:} \\
          Pipeline & method & \textsc{No} & \textsc{Yes} \\ \midrule
DWT \cite{bai2017deep} & - & 21.2 & - \\
SGN \cite{liu2017sgn} & - & 29.2 & - \\
Mask RCNN \cite{he2017mask} & - & 31.5 & - \\ \hline
 & \textbf{\algname{} Average}& \textbf{34.3}  & 33.9  \\
\multirow{2}{*}{GMIS \cite{liu2018affinity}} & MultiStepHAC \cite{liu2018affinity} & 33.0 & -  \\
 % & \algname{} Max &   24.3  &   32.5  \\
 & \algname{} Abs. Max. \cite{wolf2018mutex}  & 32.1 & 32.1 \\
 & \algname{} Sum \cite{keuper2015efficient,levinkov2017comparative} & 31.3  & 31.9  \\
 % & \algname{} Min &  0    & 0  \\
        \end{tabular}
    \captionof{table}{Average Precision (AP) scores (higher is better) on the CityScapes validation set.}
    \label{tab:results_cityscapes_val}
\end{minipage}\hfill
\begin{minipage}[b]{0.46\textwidth}
    \centering
\includegraphics[width=\textwidth]{./figs/cityscapes_compare_3.pdf} % left bottom right top
\caption{Instance segmentations given by different \algname{} linkage criteria on CityScapes}\label{fig:cityscapes}
\end{minipage}
\end{figure}

### 2019-05-23 chapters/5_experiments_compare_rules.tex
Update tables

\subsection{Data and methods} \label{sec:cremi_challenge}
We evaluate the algorithms in our framework on the competitive CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge} that is currently the neuron segmentation challenge with the largest amount of training data available. The dataset comes from serial section EM of \emph{Drosophila} fruit-fly tissue and consists of 6 volumes of 1250x1250x125 voxels at resolution 4x4x40nm, three of which present publicly available training ground truth. The results submitted to the leaderboard are evaluated using the CREMI score (\url{https://cremi.org/leaderboard/}), based on the Adapted Rand-Score (Rand-Score) and the Variation of Information Score \cite{arganda2015crowdsourcing}. In Appendix \ref{sec:cremi_details}, we provide more details about the training of our CNN model, inspired by work of \cite{lee2017superhuman,funke2018large}.

\textbf{State-of-the-art methods } We compare the performances of \algname{} with other basic and state-of-the-art post-processing methods. To ensure a fair comparison, we test all methods on the same predictions of our CNN model. As basic method, we perform a simple thresholding (THRESH) by running connected components on a boundary map generated from the CNN affinities (see Appendix \ref{sec:cremi_details} for more details on this and the following methods). On the other hand, most of state-of-the-art methods for neuron-segmentation first generates 2D superpixels and then apply a graph partitioning algorithm, since this approach so far proved to be the most reliable that could scale up to the size of the problem. Superpixels are usually computed with a watershed algorithm seeded at the maxima of a boundary distance transform (WSDT). The algorithms employed in our comparison to partition the superpixel graph were given by approximations of the multicut (WSDT+MC) and lifted multicut (WSDT+LMC) problems.

>>>>

\subsection{Data: CREMI challenge} \label{sec:cremi_challenge}
We evaluate the algorithms in our framework on the competitive CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge} that is currently the neuron segmentation challenge with the largest amount of training data available. The dataset comes from serial section EM of \emph{Drosophila} fruit-fly tissue and consists of 6 volumes of 1250x1250x125 voxels at resolution 4x4x40nm, three of which present publicly available training ground truth. The results submitted to the leaderboard are evaluated using the CREMI score (\url{https://cremi.org/leaderboard/}), based on the Adapted Rand-Score (Rand-Score) and the Variation of Information Score \cite{arganda2015crowdsourcing}. In Appendix \ref{sec:cremi_details}, we provide more details about the training of our CNN model, inspired by work of \cite{lee2017superhuman,funke2018large}.

### 2019-05-23 chapters/5_experiments_noise.tex
Update tables

\subsection{Results and discussion}\label{sec:results}
% \subsection{In-depth comparison of different linkage criteria for \algname{}} 
\textbf{Comparison results } Table \ref{tab:results_cremi_train} shows how \algname{} compares to other tested post-processing methods applied to the predictions of our model. 
% The poor scores achieved by THRESH highlight the difficulty of the task. 
\algname{} with \emph{Average} linkage, representing one of the new algorithms introduced by our generalized framework, significantly outperformed all other previously proposed agglomerative methods like GAEC, Greedy Fixation (using \emph{Sum} linkage) or Mutex Watershed (using \emph{Abs Max} linkage). The competitive performances of this simple parameter-free agglomerative algorithm are also reported by Table \ref{tab:results_cremi_test} that represents the current leader-board of the challenge: all entries, apart from \algname{}, employ superpixel-based post-processing pipelines, several of which rely on the complex multicut problem. 
In the comparison shown in Table \ref{tab:results_cremi_train}, \algname{} with \emph{Average} linkage even achieved superior scores compared to other methods based on WSDT superpixels.
This shows that this method offers a simple and successful approach growing clusters starting directly from pixels and had the advantage of avoiding potential errors in the superpixel generation. In fact, generating for example good quality WSDT superpixels requires to tune several parameters.   
%Our hypothesis to explain this superior performances is that, currently, there are not good ways of generating superpixels that can take the long-range predictions of the CNN into account. 
%It is of course possible to make use of long-range predictions to compute the edge weights of the superpixel graph, but, in our experience, this process usually involves a lot of parameter tuning and trial and error. 
Moreover, superpixel generation does not usually make use of the long-range predictions of the CNN and, in our experiments, using them to compute the weights of the edges in the superpixel graph did not change the final scores.
Fig. \ref{fig:cremi_comparison} highlights some failure cases of the different agglomerative algorithms included in our framework.
In Appendix \ref{sec:appendix_exps_full_cremi}, we provide more details about how we scaled up \algname{} to the full datasets. Appendix Table \ref{tab:extended_results_cremi} lists the performances and the run-times for all tested \algname{} linkage.

\begin{figure}[t]
        \centering
\begin{minipage}[t]{0.56\textwidth}
% \begin{table}
    \centering
    \scriptsize
    % \begin{subtable}[t!]{0.5\textwidth}\centering
        \begin{tabular}[t]{l|l|c}
        % \toprule
        % & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
         % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
         & \makecell[l]{\algname{}\\ Linkage} & \makecell{CREMI-Score \\(lower is better)} \\ \midrule 
         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
\textbf{Our UNet + \algname{} Avg-Link} & \textbf{Average}& \textbf{0.226}  \\
Our UNet + Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr. & 0.282 \\
Our UNet + DTWS + MC & -& 0.310 \\
Our UNet + DTWS + LMC & -& 0.317 \\
Our UNet + Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & 0.322 \\
Our UNet + GAEC \cite{keuper2015efficient} & Sum & 0.334 \\
Our UNet + THRESH &-& 1.521 \\ 
% \textbf{\algname{}} & \textbf{Average}& \textbf{0.936 $\pm$ 0.004}  \\
% Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr. & 0.906 $\pm$ 0.022 \\
% DTWS + LMC & -& 0.903 $\pm$ 0.016 \\
% DTWS + MC & -& 0.903 $\pm$ 0.017 \\
% % DTWS + avgHC &-& \\
% % DTWS + MC (SR)& -& 0.900 $\pm$ 0.019 \\
% % DTWS + LMC (SR)& -& 0.898 $\pm$ 0.017 \\
% Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & 0.897 $\pm$ 0.012 \\
% GAEC \cite{keuper2015efficient} & Sum & 0.872 $\pm$ 0.028 \\
% THRESH &-& 0.221  $\pm$ 0.067 \\ 
% % DTWS + \algname{} & Average& \TODO{} \\
% % DTWS  & -& 0.010 $\pm$ 0.003\\
        \end{tabular}
    \captionof{table}{CREMI-Scores achieved by different post-processing methods. Scores are averaged over the three CREMI training datasets}
    \label{tab:results_cremi_train}
\end{minipage}\hfill
\begin{minipage}[t]{0.4\textwidth}
    \centering
    \scriptsize
        \begin{tabular}[t]{l|c}
         & \makecell{CREMI-Score \\(lower is better)}  \\ \midrule
Our UNet + DTWS + LMC &  0.221\\
PNI-UNet \cite{lee2017superhuman} & 0.228 \\
\textbf{Our UNet + \algname{} Avg-Link} & \textbf{0.241} \\
MALA-UNet + MC \cite{funke2018large} & 0.276 \\
CRUNet \cite{zeng2017deepem3d} & 0.566  \\
LFC \cite{parag2017anisotropic} & 0.616  \\
% Our UNet + DTWS + LMC &  \textbf{0.221} & \textbf{0.108}\\
% PNI-UNet & 0.228 & 0.116 \\
% Our UNet + \algname{} Avg-Linkage & 0.244 & 0.130 \\
% MALA-UNet + MC \cite{funke2018large} & 0.276 & 0.132 \\
% CRUNet \cite{zeng2017deepem3d} & 0.566 & 0.229 \\
% LFC \cite{parag2017anisotropic} & 0.616 & \\
        \end{tabular}
        \vspace*{1.1em}
    \captionof{table}{Current published entries of the CREMI challenge leaderboard \cite{cremiChallenge} (May 2019) on the three test datasets}
    \label{tab:results_cremi_test}
\end{minipage}
\end{figure}
\captionsetup[subfigure]{justification=centering, singlelinecheck=off}
\begin{figure}
\centering
    %     \begin{subfigure}[t]{0.49 \textwidth}
    %     \centering
    %     \includegraphics[width=\textwidth,trim=0.55in 0.35in 0.65in 0.80in,clip]{./figs/merge_noise_only_direct.pdf}

>>>>

\subsection{Results and discussion}\label{sec:results}
% \subsection{In-depth comparison of different linkage criteria for \algname{}} 
\textbf{Comparison results } Table \ref{tab:results_cremi_train} shows how the agglomerative algorithms derived from our framework compare to each other. For a simple baseline, we also include a segmentation produced by thresholding the affinity predictions (THRESH).
% The poor scores achieved by THRESH highlight the difficulty of the task. 
\algname{} with \emph{Average} linkage, representing one of the new algorithms introduced by our generalized framework, significantly outperformed all other previously proposed agglomerative methods like GAEC, Greedy Fixation (using \emph{Sum} linkage) or Mutex Watershed (using \emph{Abs Max} linkage). The competitive performances of this simple parameter-free agglomerative algorithm are also reported by Table \ref{tab:results_cremi_test} that represents the current leader-board of the challenge: all entries, apart from \algname{}, employ superpixel-based post-processing pipelines, several of which rely on the complex multicut problem of \cite{beier2017multicut} that uses several random forests to predict graph edge weights, relying not only on information derived from affinity maps but also raw data and shape information.
Note that the test volumes contain several imaging artifacts that make segmentation particularly challenging and might profit from more robust edge statistics of super-pixel based approaches.
On the other hand, the fact that our algorithm can operate on pixels directly removes the parameter tuning necessary to obtain good super-pixels and can also avoid errors that result from wrong superpixels that cannot be fixed during later agglomeration.
In Appendix \ref{sec:appendix_exps_full_cremi}, we provide more details about how we scaled up \algname{} to the full datasets. Appendix Table \ref{tab:extended_results_cremi} lists the performances and the run-times for all tested \algname{} linkage.

\begin{figure}[t]
        \centering
\begin{minipage}[t]{0.56\textwidth}
% \begin{table}
    \centering
    \scriptsize
    % \begin{subtable}[t!]{0.5\textwidth}\centering
        \begin{tabular}[t]{l|c}
        % \toprule
        % & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
         % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
          & \makecell{CREMI-Score \\(lower is better)} \\ \midrule 
         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
\textbf{Our UNet + \algname{}} \textbf{Average}& \textbf{0.226}  \\
Our UNet + \algname{} Sum + Constraints \cite{levinkov2017comparative} & 0.282 \\
% Our UNet + DTWS + MC & -& 0.310 \\
% Our UNet + DTWS + LMC & -& 0.317 \\
Our UNet + \algname{} Abs. Max. \cite{wolf2018mutex} & 0.322 \\
Our UNet + \algname{} Max. + Constraints & 0.324 \\
Our UNet + \algname{} Sum \cite{keuper2015efficient} & 0.334 \\
Our UNet + \algname{} Average + Constraints & 0.563 \\
Our UNet + THRESH & 1.521 \\ 
Our UNet + \algname{} Min & 2.522 \\
Our UNet + \algname{} Min + Constraints & 2.522 \\
Our UNet + \algname{} Max & 2.626 \\
% \textbf{\algname{}} & \textbf{Average}& \textbf{0.936 $\pm$ 0.004}  \\
% Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr. & 0.906 $\pm$ 0.022 \\
% DTWS + LMC & -& 0.903 $\pm$ 0.016 \\
% DTWS + MC & -& 0.903 $\pm$ 0.017 \\
% % DTWS + avgHC &-& \\
% % DTWS + MC (SR)& -& 0.900 $\pm$ 0.019 \\
% % DTWS + LMC (SR)& -& 0.898 $\pm$ 0.017 \\
% Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & 0.897 $\pm$ 0.012 \\
% GAEC \cite{keuper2015efficient} & Sum & 0.872 $\pm$ 0.028 \\
% THRESH &-& 0.221  $\pm$ 0.067 \\ 
% % DTWS + \algname{} & Average& \TODO{} \\
% % DTWS  & -& 0.010 $\pm$ 0.003\\
        \end{tabular}
    \captionof{table}{CREMI-Scores achieved by different post-processing methods. Scores are averaged over the three CREMI training datasets}
    \label{tab:results_cremi_train}
\end{minipage}\hfill
\begin{minipage}[t]{0.4\textwidth}
    \centering
    \scriptsize
        \begin{tabular}[t]{l|c}
         & \makecell{CREMI-Score \\(lower is better)}  \\ \midrule
Our UNet + DTWS + LMC &  0.221\\
PNI-UNet \cite{lee2017superhuman} & 0.228 \\
\textbf{Our UNet + \algname{} Average} & \textbf{0.241} \\
MALA-UNet + MC \cite{funke2018large} & 0.276 \\
CRUNet \cite{zeng2017deepem3d} & 0.566  \\
LFC \cite{parag2017anisotropic} & 0.616  \\
% Our UNet + DTWS + LMC &  \textbf{0.221} & \textbf{0.108}\\
% PNI-UNet & 0.228 & 0.116 \\
% Our UNet + \algname{} Avg-Linkage & 0.244 & 0.130 \\
% MALA-UNet + MC \cite{funke2018large} & 0.276 & 0.132 \\
% CRUNet \cite{zeng2017deepem3d} & 0.566 & 0.229 \\
% LFC \cite{parag2017anisotropic} & 0.616 & \\
        \end{tabular}
        % \vspace*{1.1em}
    \captionof{table}{Current published entries of the CREMI challenge leaderboard \cite{cremiChallenge} (May 2019) on the three test datasets}
    \label{tab:results_cremi_test}
\end{minipage}
\end{figure}
\captionsetup[subfigure]{justification=centering, singlelinecheck=off}
\begin{figure}
\centering
    %     \begin{subfigure}[t]{0.49 \textwidth}
    %     \centering
    %     \includegraphics[width=\textwidth,trim=0.55in 0.35in 0.65in 0.80in,clip]{./figs/merge_noise_only_direct.pdf}
